\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Three spelling fixes

\noindent
As the first and third columns are suppressed, \ttt{comm} can be categorized in \sta by regarding its first file argument as a static ``configuration'' input;
% NV: I don't think this is correct, because the small input might be the other argument;  you could even have `comm - -`
  this input accompanies every replicated instance of the command executing in parallel.
The second clause is symmetric to the first with respect to the second input. 
The third clause is the general case, classifiying \ttt{comm} in \pur, as \ttt{comm} needs to read both inputs completely before outputing its results.
Option \ttt{stdin-hyphen} indicates that \ttt{-} represents standard input if given as a file argument, and option \ttt{short-combined} indicates that flags can be combined, as in \ttt{comm -13}.
% The third clause is the general case, which includes \ttt{comm} invocations without any options, and is captured by the third clause.
% There, \ttt{comm} is classified as \pur as it needs to % wait until it 
%   read both inputs completely before it can output its results.
% Its inputs are its first and second file arguments (\ie excluding any options), and its output is produced in \ttt{stdout}.

@@

Developed independently and at the same time with \sys, POSH~\cite{raghavan2020posh} is a framework for running shell scripts over remote storage by offloading the I/O-intensive portions to proxy servers closer to the data.
POSH focuses on co-locating distributed operation, and introduces a novel scheduling algorithm. 
\sys instead focuses on the parallelization of CPU-intensive scripts, by transforming them to DFGs, applying transformations, and then transforming them back to parallel schell scripts augmented with \sys's runtime primitives to be executed on a standard shell.
%  non-distributed parallelism, is location-agnostic, and focuses on correctness through its dataflow transformations.

>>>>

\noindent
As the first and third columns are suppressed, \ttt{comm} can be categorized in \sta by regarding its first file argument as a static ``configuration'' input;
% NV: I don't think this is correct, because the small input might be the other argument;  you could even have `comm - -`
  this input accompanies every replicated instance of the command executing in parallel.
The second clause is symmetric to the first with respect to the second input. 
The third clause is the general case, classifying \ttt{comm} in \pur, as \ttt{comm} needs to read both inputs completely before outputting its results.
Option \ttt{stdin-hyphen} indicates that \ttt{-} represents standard input if given as a file argument, and option \ttt{short-combined} indicates that flags can be combined, as in \ttt{comm -13}.
% The third clause is the general case, which includes \ttt{comm} invocations without any options, and is captured by the third clause.
% There, \ttt{comm} is classified as \pur as it needs to % wait until it 
%   read both inputs completely before it can output its results.
% Its inputs are its first and second file arguments (\ie excluding any options), and its output is produced in \ttt{stdout}.

@@

Developed independently and at the same time with \sys, POSH~\cite{raghavan2020posh} is a framework for running shell scripts over remote storage by offloading the I/O-intensive portions to proxy servers closer to the data.
POSH focuses on co-locating distributed operation, and introduces a novel scheduling algorithm. 
\sys instead focuses on the parallelization of CPU-intensive scripts, by transforming them to DFGs, applying transformations, and then transforming them back to parallel shell scripts augmented with \sys's runtime primitives to be executed on a standard shell.
%  non-distributed parallelism, is location-agnostic, and focuses on correctness through its dataflow transformations.
